Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-28 paper_comparison/appendix.Rmd
update table in appendix

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(pronoun) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(Pronoun = pronoun) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "pronoun", caption = "Summary of pronoun distribution of subjects recuritted in this study.")
```

@@

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(education) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp, values_fill = 0) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  slice(c(2, 1, 3, 4, 5)) %>%
  rename(`Education` = education) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "education", caption = "Summary of education distribution of subjects recuritted in this study.")
```

>>>>

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(pronoun) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(Pronoun = pronoun) %>%
  add_row(Pronoun = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(Pronoun, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Pronoun", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"), 
                    booktabs = TRUE, label = "pronoun", caption = "Summary of pronoun distribution of subjects recuritted in this study.")
```

@@

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(education) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp, values_fill = 0) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  slice(c(2, 1, 3, 4, 5)) %>%
  rename(`Education` = education) %>%
  add_row(`Education` = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I` = paste0(`Period I`, " (", round(`Period I`/443*100, 1), "%)")) %>%
  mutate(`Period II` = paste0(`Period II`, " (", round(`Period II`/443*100, 1), "%)")) %>%
  mutate(`Period III` = paste0(`Period III`, " (", round(`Period III`/443*100, 1), "%)")) %>%
  mutate(Total = paste0(Total, " (", round(Total/443*100, 1), "%)")) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "education", caption = "Summary of education distribution of subjects recuritted in this study.")
```
